Deviance in a generalized linear model

### 2024-07-06 text/21/anonymizing-ids.Rmd
Updated 2022 Rmd files

```{r, echo=FALSE}
suppressMessages(suppressWarnings(library(dplyr)))
suppressMessages(suppressWarnings(library(knitr)))
suppressMessages(suppressWarnings(library(kableExtra)))
suppressMessages(suppressWarnings(library(magrittr)))
private_id <- 12345678+(0:7)*11262783
data.frame(private_id=private_id) %>%
  kbl %>%
  kable_minimal(full_width=FALSE, position="left")
```

@@

```{r, echo=FALSE}
e <- data.frame(private_id=as.character(private_id), random_id=as.character(private_id+480035489))
e %>%
  kbl %>%
  kable_minimal(full_width=FALSE, position="left")
```

@@

```{r, echo=FALSE}
d <- data.frame(
  private_id=c(rep(private_id[1:3], c(4, 3, 2)), "..."),
  report_date=c(as.character(Sys.Date()-round(runif(9, 0, 60))), "..."),
  data=c(round(runif(9, 100, 199)), "..."))
d %>%
  kbl %>%
  kable_minimal(full_width=FALSE, position="left")
```

@@

```{r, echo=FALSE}
e %>%
  bind_rows(data.frame(private_id="...", random_id="...")) -> f
merge(f, d) -> g
# g <- g[c(2:9, 1), ]
h <- g[c(2:9, 1), ]
h %>%
  tibble %>%
  data.frame %>%
  kbl %>%
  kable_minimal(full_width=FALSE, position="left")
```

@@

```{r, echo=FALSE}
h %>%
  select(-private_id) %>%
  kbl %>%
  kable_minimal(full_width=FALSE, position="left")
```

>>>>

```{r anonymizing-ids-01, echo=FALSE}
suppressMessages(suppressWarnings(library(dplyr)))
suppressMessages(suppressWarnings(library(knitr)))
suppressMessages(suppressWarnings(library(kableExtra)))
suppressMessages(suppressWarnings(library(magrittr)))
private_id <- 12345678+(0:7)*11262783
data.frame(private_id=private_id) %>%
  kbl %>%
  kable_minimal(full_width=FALSE, position="left")
```

@@

```{r anonymizing-ids-02, echo=FALSE}
e <- data.frame(private_id=as.character(private_id), random_id=as.character(private_id+480035489))
e %>%
  kbl %>%
  kable_minimal(full_width=FALSE, position="left")
```

@@

```{r anonymizing-ids-03, echo=FALSE}
d <- data.frame(
  private_id=c(rep(private_id[1:3], c(4, 3, 2)), "..."),
  report_date=c(as.character(Sys.Date()-round(runif(9, 0, 60))), "..."),
  data=c(round(runif(9, 100, 199)), "..."))
d %>%
  kbl %>%
  kable_minimal(full_width=FALSE, position="left")
```

@@

```{r anonymizing-ids-04, echo=FALSE}
e %>%
  bind_rows(data.frame(private_id="...", random_id="...")) -> f
merge(f, d) -> g
# g <- g[c(2:9, 1), ]
h <- g[c(2:9, 1), ]
h %>%
  tibble %>%
  data.frame %>%
  kbl %>%
  kable_minimal(full_width=FALSE, position="left")
```

@@

```{r anonymizing-ids-05, echo=FALSE}
h %>%
  select(-private_id) %>%
  kbl %>%
  kable_minimal(full_width=FALSE, position="left")
```

### 2024-07-06 text/21/cubic-splines.Rmd
Updated 2022 Rmd files

```{r setup}
suppressMessages(suppressWarnings(library(broom)))
suppressMessages(suppressWarnings(library(dplyr)))
suppressMessages(suppressWarnings(library(Hmisc)))
suppressMessages(suppressWarnings(library(knitr)))
suppressMessages(suppressWarnings(library(magrittr)))
suppressMessages(suppressWarnings(library(rms)))
suppressMessages(suppressWarnings(library(splines)))
suppressMessages(suppressWarnings(library(tidyr)))
```

@@

```{r}
library(ggplot2)
x <- 0:20
y <- rep(40, 21)
y[6:21] <- y[6:21]-3*(0:15)
y[11:21] <- y[11:21]+7*(0:10)
y[16:21] <- y[16:21]-(0:5)^2
y <- y+round(rnorm(21), 1)
simulated_example <- data.frame(x, y)
simulated_example
ggplot(simulated_example, aes(x, y)) +
  geom_point()
```

@@

```{r}
x <- c(0:20, setdiff(seq(0, 20, by=1/64), 0:20))
```

@@

```{r}
xm <- data.frame(
  c1 =rep(1, length(x)),
  c2 =x,
  c3 =x^2,
  c4 =x^3,
  c5 =(x> 5)*rep(1, length(x)),
  c6 =(x> 5)*(x- 5),
  c7 =(x> 5)*(x- 5)^2,
  c8 =(x> 5)*(x- 5)^3,
  c9 =(x>10)*rep(1, length(x)),
  c10=(x>10)*(x-10),
  c11=(x>10)*(x-10)^2,
  c12=(x>10)*(x-10)^3,
  c13=(x>15)*rep(1, length(x)),
  c14=(x>15)*(x-15),
  c15=(x>15)*(x-15)^2,
  c16=(x>15)*(x-15)^3,
  x=x,
  y=NA
)
xm$y[1:21] <- y
```

@@

```{r}
kable(xm[1:21, 1:16])
```

@@

```{r}
display_curve <- function(dat, lb) {
  # Plot a line connecting the points in dat
  # Assume that column 1 is x and column 2 is y
  # Work with either a data frame or matrix
  dat %>%
    data.frame %>%
    select(1:2) %>%
    set_names(c("x", "y")) %>%
    ggplot(aes(x, y)) +
      ggtitle(lb) +
      geom_line() +
      xlab(" ") +
      ylab(" ")
}

@@

```{r}

@@

```{r}
lm(y~c2+c3+c4+c5+c6+c7+c8+c9+c10+c11+c12+c13+c14+c15+c16, data=xm)  %>%
  augment(newdata=xm) %>%
  select(c2, .fitted) %>%
    display_curve("Discontinous cubic splines") %>%
    display_dots(simulated_example)
```

@@

```{r}
lm(y~c2+c3+c4+c6+c7+c8+c10+c11+c12+c14+c15+c16, data=xm)  %>%
  augment(newdata=xm) %>%
  select(c2, .fitted) %>%
    display_curve("Continuous but not smooth cubic splines") %>%
    display_dots(simulated_example)
```

@@

```{r}
lm(y~c2+c3+c4+c7+c8+c11+c12+c15+c16, data=xm) %>%
  augment(newdata=xm) %>%
  select(c2, .fitted) %>%
    display_curve("Continuous and smooth (1st derivative) cubic splines") %>%
    display_dots(simulated_example)
```

@@

```{r}
lm(y~c2+c3+c4+c8+c12+c16, data=xm) %>%
  augment(newdata=xm) %>%
  select(c2, .fitted) %>%
    display_curve("Continous and smooth (1st and 2nd derivatives) cubic splines") %>%
    display_dots(simulated_example)
```

@@

```{r}
round(cor(xm[c(2:4, 8, 12, 16)]), 2)
```

@@

```{r}
cubic_spline <- bs(xm$c2, knots=c(5, 10, 15), degree=3, intercept=TRUE)
```

@@

```{r}
for (j in 1:dim(cubic_spline)[2]) {
  dat <- cbind(xm$c2, cubic_spline[ , j])
  display_curve(dat, "Cubic B-spline terms") %>%
    display_dots(dat[1:21, ]) %>%
    plot
}
```

@@

```{r}
round(cor(cubic_spline), 1)
```

@@

```{r}
lm(xm$y~cubic_spline) %>%
  augment(newdata=xm) %>%
  select(c2, .fitted) %>%
    display_curve("Cubic spline fit to the data") %>%
    display_dots(simulated_example)
```

@@

```{r}
linear_spline <- bs(xm$c2, knots=c(5, 10, 15), degree=1, intercept=TRUE)
```

@@

```{r}
for (j in 1:dim(linear_spline)[2]) {
  dat <- cbind(xm$c2, linear_spline[ , j])
  display_curve(dat, "Linear B-spline terms") %>%
    display_dots(dat[1:21, ]) %>%
    plot
}
```

@@

```{r}
lm(xm$y~linear_spline) %>%
  augment(newdata=xm) %>%
  select(c2, .fitted) %>%
    display_curve("Linear spline fit to the data") %>%
    display_dots(simulated_example)
```

@@

```{r}
quadratic_spline <- bs(xm$c2, knots=c(5, 10, 15), degree=2, intercept=TRUE)
kable(quadratic_spline[1:21, ])
```

@@

```{r}
for (j in 1:dim(quadratic_spline)[2]) {
  dat <- cbind(xm$c2, quadratic_spline[ , j])
  display_curve(dat, "Quadratic B-spline terms") %>%
    display_dots(dat[1:21, ]) %>%
    plot
}
```

@@

```{r}
lm(xm$y~quadratic_spline) %>%
  augment(newdata=xm) %>%
  select(c2, .fitted) %>%
    display_curve("Quadratic spline fit to the data") %>%
    display_dots(simulated_example)
```

@@

```{r}
natural_spline <- ns(xm$c2, knots=c(5, 10, 15), intercept=TRUE)
kable(natural_spline[1:21, ])
```

@@

```{r}
extended_x <- seq(-5, 25, by=1/64)
extended_spline <- predict(natural_spline, extended_x)
for (j in 1:dim(extended_spline)[2]) {
  dat <- cbind(extended_x, extended_spline[ , j])
  spline_dots <- cbind(0:20, extended_spline[extended_x %in% 0:20, j])
  display_curve(dat, "Natural spline terms") %>%
    display_dots(spline_dots) %>%
    plot
}
```

@@

```{r}
extended_y <- rep(NA, length(extended_x))
extended_y[extended_x %in% 0:20] <- simulated_example$y
lm(extended_y~extended_spline) %>%
  augment(newdata=extended_spline) %>%
  data.frame(c2=extended_x) %>%
  select(c2, .fitted) %>%
    display_curve("Natural spline fit to the data") %>%
    display_dots(simulated_example)
```

@@

```{r}
for (k in 3:7) {
  knots <- 20*((1:k)-0.5)/k
  lm(y~bs(c2, knots=knots), data=xm) -> rcs_fit
  # lm(y~rcs(c2, k), data=xm) -> rcs_fit
  ti <- paste0(k, " knots, AIC = ", round(AIC(rcs_fit), 1), ", BIC = ", round(BIC(rcs_fit), 1))
  rcs_fit %>%
    augment(newdata=xm) %>%
    select(c2, .fitted) %>%
      display_curve(ti) %>%
      display_dots(simulated_example) -> cplot
    plot(cplot + geom_vline(xintercept=knots, color="black", linetype="dotted"))
}
```

@@

```{r}
for (k in 3:7) {
  knots <- k + c(0, 5, 10)
  lm(y~bs(c2, knots=knots), data=xm) -> rcs_fit
  # lm(y~rcs(c2, k), data=xm) -> rcs_fit
  ti <- paste0("Knots at ", paste(knots, collapse=", "))
  rcs_fit %>%
    augment(newdata=xm) %>%
    select(c2, .fitted) %>%
      display_curve(ti) %>%
      display_dots(simulated_example) -> cplot
    plot(cplot + geom_vline(xintercept=knots, color="black", linetype="dotted"))
}
```

>>>>

```{r cubic-splines-01}
suppressMessages(suppressWarnings(library(broom)))
suppressMessages(suppressWarnings(library(dplyr)))
suppressMessages(suppressWarnings(library(Hmisc)))
suppressMessages(suppressWarnings(library(knitr)))
suppressMessages(suppressWarnings(library(magrittr)))
suppressMessages(suppressWarnings(library(rms)))
suppressMessages(suppressWarnings(library(splines)))
suppressMessages(suppressWarnings(library(tidyr)))
```

@@

```{r cubic-splines-02}
library(ggplot2)
x <- 0:20
y <- rep(40, 21)
y[6:21] <- y[6:21]-3*(0:15)
y[11:21] <- y[11:21]+7*(0:10)
y[16:21] <- y[16:21]-(0:5)^2
y <- y+round(rnorm(21), 1)
simulated_example <- data.frame(x, y)
simulated_example
ggplot(simulated_example, aes(x, y)) +
  geom_point()
```

@@

```{r cubic-splines-03}
x <- c(0:20, setdiff(seq(0, 20, by=1/64), 0:20))
```

@@

```{r cubic-splines-04}
xm <- data.frame(
  c1 =rep(1, length(x)),
  c2 =x,
  c3 =x^2,
  c4 =x^3,
  c5 =(x> 5)*rep(1, length(x)),
  c6 =(x> 5)*(x- 5),
  c7 =(x> 5)*(x- 5)^2,
  c8 =(x> 5)*(x- 5)^3,
  c9 =(x>10)*rep(1, length(x)),
  c10=(x>10)*(x-10),
  c11=(x>10)*(x-10)^2,
  c12=(x>10)*(x-10)^3,
  c13=(x>15)*rep(1, length(x)),
  c14=(x>15)*(x-15),
  c15=(x>15)*(x-15)^2,
  c16=(x>15)*(x-15)^3,
  x=x,
  y=NA
)
xm$y[1:21] <- y
```

@@

```{r cubic-splines-05}
kable(xm[1:21, 1:16])
```

@@

```{r cubic-splines-06}
display_curve <- function(dat, lb) {
  # Plot a line connecting the points in dat
  # Assume that column 1 is x and column 2 is y
  # Work with either a data frame or matrix
  dat %>%
    data.frame %>%
    select(1:2) %>%
    set_names(c("x", "y")) %>%
    ggplot(aes(x, y)) +
      ggtitle(lb) +
      geom_line() +
      xlab(" ") +
      ylab(" ")
}

@@

```{r cubic-splines-07}

@@

```{r cubic-splines-08}
lm(y~c2+c3+c4+c5+c6+c7+c8+c9+c10+c11+c12+c13+c14+c15+c16, data=xm)  %>%
  augment(newdata=xm) %>%
  select(c2, .fitted) %>%
    display_curve("Discontinous cubic splines") %>%
    display_dots(simulated_example)
```

@@

```{r cubic-splines-09}
lm(y~c2+c3+c4+c6+c7+c8+c10+c11+c12+c14+c15+c16, data=xm)  %>%
  augment(newdata=xm) %>%
  select(c2, .fitted) %>%
    display_curve("Continuous but not smooth cubic splines") %>%
    display_dots(simulated_example)
```

@@

```{r cubic-splines-10}
lm(y~c2+c3+c4+c7+c8+c11+c12+c15+c16, data=xm) %>%
  augment(newdata=xm) %>%
  select(c2, .fitted) %>%
    display_curve("Continuous and smooth (1st derivative) cubic splines") %>%
    display_dots(simulated_example)
```

@@

```{r cubic-splines-11}
lm(y~c2+c3+c4+c8+c12+c16, data=xm) %>%
  augment(newdata=xm) %>%
  select(c2, .fitted) %>%
    display_curve("Continous and smooth (1st and 2nd derivatives) cubic splines") %>%
    display_dots(simulated_example)
```

@@

```{r cubic-splines-12}
round(cor(xm[c(2:4, 8, 12, 16)]), 2)
```

@@

```{r cubic-splines-13}
cubic_spline <- bs(xm$c2, knots=c(5, 10, 15), degree=3, intercept=TRUE)
```

@@

```{r cubic-splines-14}
for (j in 1:dim(cubic_spline)[2]) {
  dat <- cbind(xm$c2, cubic_spline[ , j])
  display_curve(dat, "Cubic B-spline terms") %>%
    display_dots(dat[1:21, ]) %>%
    plot
}
```

@@

```{r cubic-splines-15}
round(cor(cubic_spline), 1)
```

@@

```{r cubic-splines-16}
lm(xm$y~cubic_spline) %>%
  augment(newdata=xm) %>%
  select(c2, .fitted) %>%
    display_curve("Cubic spline fit to the data") %>%
    display_dots(simulated_example)
```

@@

```{r cubic-splines-17}
linear_spline <- bs(xm$c2, knots=c(5, 10, 15), degree=1, intercept=TRUE)
```

@@

```{r cubic-splines-18}
for (j in 1:dim(linear_spline)[2]) {
  dat <- cbind(xm$c2, linear_spline[ , j])
  display_curve(dat, "Linear B-spline terms") %>%
    display_dots(dat[1:21, ]) %>%
    plot
}
```

@@

```{r cubic-splines-19}
lm(xm$y~linear_spline) %>%
  augment(newdata=xm) %>%
  select(c2, .fitted) %>%
    display_curve("Linear spline fit to the data") %>%
    display_dots(simulated_example)
```

@@

```{r cubic-splines-20}
quadratic_spline <- bs(xm$c2, knots=c(5, 10, 15), degree=2, intercept=TRUE)
kable(quadratic_spline[1:21, ])
```

@@

```{r cubic-splines-21}
for (j in 1:dim(quadratic_spline)[2]) {
  dat <- cbind(xm$c2, quadratic_spline[ , j])
  display_curve(dat, "Quadratic B-spline terms") %>%
    display_dots(dat[1:21, ]) %>%
    plot
}
```

@@

```{r cubic-splines-22}
lm(xm$y~quadratic_spline) %>%
  augment(newdata=xm) %>%
  select(c2, .fitted) %>%
    display_curve("Quadratic spline fit to the data") %>%
    display_dots(simulated_example)
```

@@

```{r cubic-splines-23}
natural_spline <- ns(xm$c2, knots=c(5, 10, 15), intercept=TRUE)
kable(natural_spline[1:21, ])
```

@@

```{r cubic-splines-24}
extended_x <- seq(-5, 25, by=1/64)
extended_spline <- predict(natural_spline, extended_x)
for (j in 1:dim(extended_spline)[2]) {
  dat <- cbind(extended_x, extended_spline[ , j])
  spline_dots <- cbind(0:20, extended_spline[extended_x %in% 0:20, j])
  display_curve(dat, "Natural spline terms") %>%
    display_dots(spline_dots) %>%
    plot
}
```

@@

```{r cubic-splines-25}
extended_y <- rep(NA, length(extended_x))
extended_y[extended_x %in% 0:20] <- simulated_example$y
lm(extended_y~extended_spline) %>%
  augment(newdata=extended_spline) %>%
  data.frame(c2=extended_x) %>%
  select(c2, .fitted) %>%
    display_curve("Natural spline fit to the data") %>%
    display_dots(simulated_example)
```

@@

```{r cubic-splines-26}
for (k in 3:7) {
  knots <- 20*((1:k)-0.5)/k
  lm(y~bs(c2, knots=knots), data=xm) -> rcs_fit
  # lm(y~rcs(c2, k), data=xm) -> rcs_fit
  ti <- paste0(k, " knots, AIC = ", round(AIC(rcs_fit), 1), ", BIC = ", round(BIC(rcs_fit), 1))
  rcs_fit %>%
    augment(newdata=xm) %>%
    select(c2, .fitted) %>%
      display_curve(ti) %>%
      display_dots(simulated_example) -> cplot
    plot(cplot + geom_vline(xintercept=knots, color="black", linetype="dotted"))
}
```

@@

```{r cubic-splines-27}
for (k in 3:7) {
  knots <- k + c(0, 5, 10)
  lm(y~bs(c2, knots=knots), data=xm) -> rcs_fit
  # lm(y~rcs(c2, k), data=xm) -> rcs_fit
  ti <- paste0("Knots at ", paste(knots, collapse=", "))
  rcs_fit %>%
    augment(newdata=xm) %>%
    select(c2, .fitted) %>%
      display_curve(ti) %>%
      display_dots(simulated_example) -> cplot
    plot(cplot + geom_vline(xintercept=knots, color="black", linetype="dotted"))
}
```

### 2024-07-06 text/21/dark-side.Rmd
Updated 2022 Rmd files

```{r setup, echo=FALSE}
suppressMessages(suppressWarnings(library(dplyr)))
suppressMessages(suppressWarnings(library(ggplot2)))
suppressMessages(suppressWarnings(library(magrittr)))
```

```{r, fig.width=5, fig.height=5, echo=FALSE}
o <- 0.6
v <- 0.85
draw_circles <- function() {
  dx <- 1
  dy <- 0.866
  i <- seq(0, 2*pi, length=100)
  circle <- data.frame(x=sin(i), y=cos(i))
  circle %>%
    mutate(g=1) %>%
    mutate(x=x-o*dx) %>%
    mutate(y=y-o*dy) -> circle1
  circle %>%
    mutate(g=2) %>%
    mutate(x=x+o*dx) %>%
    mutate(y=y-o*dy) -> circle2
  circle %>%
    mutate(g=3) %>%
    mutate(y=y+o*dy) -> circle3

@@

```{r, fig.width=5, fig.height=5, echo=FALSE}
o <- 0.88
draw_circles() + geom_text(x=0, y=-0.1, label="Data\nScience", size=10)
```

>>>>

```{r dark-side-01, echo=FALSE}
suppressMessages(suppressWarnings(library(dplyr)))
suppressMessages(suppressWarnings(library(ggplot2)))
suppressMessages(suppressWarnings(library(magrittr)))
```

```{r dark-side-02, fig.width=5, fig.height=5, echo=FALSE}
o <- 0.6
v <- 0.85
draw_circles <- function() {
  dx <- 1
  dy <- 0.866
  i <- seq(0, 2*pi, length=100)
  circle <- data.frame(x=sin(i), y=cos(i))
  circle %>%
    mutate(g=1) %>%
    mutate(x=x-o*dx) %>%
    mutate(y=y-o*dy) -> circle1
  circle %>%
    mutate(g=2) %>%
    mutate(x=x+o*dx) %>%
    mutate(y=y-o*dy) -> circle2
  circle %>%
    mutate(g=3) %>%
    mutate(y=y+o*dy) -> circle3

@@

```{r dark-side-02, fig.width=5, fig.height=5, echo=FALSE}
o <- 0.88
draw_circles() + geom_text(x=0, y=-0.1, label="Data\nScience", size=10)
```

### 2024-07-06 text/21/direct-standardization.Rmd
Updated 2022 Rmd files

```{r setup}
suppressMessages(suppressWarnings(library(broom)))
suppressMessages(suppressWarnings(library(dplyr)))
suppressMessages(suppressWarnings(library(ggplot2)))
suppressMessages(suppressWarnings(library(magrittr)))
```

>>>>

```{r direct-standardization-01}
suppressMessages(suppressWarnings(library(broom)))
suppressMessages(suppressWarnings(library(dplyr)))
suppressMessages(suppressWarnings(library(ggplot2)))
suppressMessages(suppressWarnings(library(magrittr)))
```

### 2024-07-06 text/21/glm-deviance.Rmd
Updated 2022 Rmd files

```{r setup}
suppressMessages(suppressWarnings(library(broom)))
suppressMessages(suppressWarnings(library(dplyr)))
suppressMessages(suppressWarnings(library(foreign)))
suppressMessages(suppressWarnings(library(ggplot2)))
suppressMessages(suppressWarnings(library(magrittr)))
```

@@

```{r, eval=FALSE}
fn <- "http://faculty.missouri.edu/huangf/data/poisson/articles.csv"
articles <- read.csv(fn)
head(articles)
```

@@

```{r}
fn <- "http://www.pmean.com/00files/couart2.dta"
articles <- read.dta(fn)
head(articles)
```

@@

```{r}
fn <- "http://www.pmean.com/00files/couart2.dta"
articles <- read.dta(fn)
head(articles)
```

@@

```{r}
pois1 <- glm(art ~ fem + ment + phd + mar + kid5, family=poisson, data = articles)
summary(pois1)

@@

```{r}
ggplot(rd, aes(r)) +
  geom_histogram(bin_width=0.2)
```

```{r}
ggplot(rd, aes(p, r)) +
  geom_point()
```

```{r}
ggplot(rd, aes(fem, r)) +
  geom_point()
```

```{r}
ggplot(rd, aes(ment, r)) +
  geom_point()
```

```{r}
ggplot(rd, aes(phd, r)) +
  geom_point()
```

```{r}
ggplot(rd, aes(mar, r)) +
  geom_point()
```

```{r}
ggplot(rd, aes(kid5, r)) +
  geom_point()
```

>>>>

```{r glm-deviance-01}
suppressMessages(suppressWarnings(library(broom)))
suppressMessages(suppressWarnings(library(dplyr)))
suppressMessages(suppressWarnings(library(foreign)))
suppressMessages(suppressWarnings(library(ggplot2)))
suppressMessages(suppressWarnings(library(magrittr)))
```

@@

```{r glm-deviance-02, eval=FALSE}
fn <- "http://faculty.missouri.edu/huangf/data/poisson/articles.csv"
articles <- read.csv(fn)
head(articles)
```

@@

```{r glm-deviance-03}
fn <- "http://www.pmean.com/00files/couart2.dta"
articles <- read.dta(fn)
head(articles)
```

@@

```{r glm-deviance-04}
fn <- "http://www.pmean.com/00files/couart2.dta"
articles <- read.dta(fn)
head(articles)
```

@@

```{r glm-deviance-05}
pois1 <- glm(art ~ fem + ment + phd + mar + kid5, family=poisson, data = articles)
summary(pois1)

@@

```{r glm-deviance-06}
ggplot(rd, aes(r)) +
  geom_histogram(bin_width=0.2)
```

```{r glm-deviance-07}
ggplot(rd, aes(p, r)) +
  geom_point()
```

```{r glm-deviance-08}
ggplot(rd, aes(fem, r)) +
  geom_point()
```

```{r glm-deviance-09}
ggplot(rd, aes(ment, r)) +
  geom_point()
```

```{r glm-deviance-10}
ggplot(rd, aes(phd, r)) +
  geom_point()
```

```{r glm-deviance-11}
ggplot(rd, aes(mar, r)) +
  geom_point()
```

```{r glm-deviance-12}
ggplot(rd, aes(kid5, r)) +
  geom_point()
```
